Physcraper: Body

### 2020-07-30 1-abstract.Rmd

1. Phylogenies are a key part of research in many areas of biology. Tools that automatize
some parts of the process of phylogenetic reconstruction, mainly molecular character matrix assembly,
have been developed for the advantage of both specialists in the field of phylogenetics and nonspecialists.
However, interpretation of results, comparison with previously available phylogenetic
hypotheses, and choosing of one phylogeny for downstream analyses and discussion still impose difficulties
to one that is not a specialist either on phylogenetic methods or on a particular group of study.

1. Physcraper is a command-line Python program that automatizes the update of published
phylogenies by enriching underlying gene alignments with public DNA sequence data. It builds upon tools from the Open Tree of Life project to link taxonomic information across databases, providing a framework for straightforward comparison of published phylogenies with their updated versions.
<!-- the conflict Application Programming Interface (API) function of  the Open Tree of Life project-->

>>>>

1. Phylogenies are a key part of research in many areas of biology. Tools that automate
some parts of the process of phylogenetic reconstruction, mainly molecular character matrix assembly,
have been developed for the advantage of both specialists in the field of phylogenetics and nonspecialists.
However, interpretation of results, comparison with previously available phylogenetic
hypotheses, and choosing of one phylogeny for downstream analyses and discussion still impose difficulties
to one that is not a specialist either on phylogenetic methods or on a particular group of study.

1. Physcraper is a command-line Python program that automates the update of published
phylogenies by enriching underlying gene alignments with public DNA sequence data. It builds upon tools from the Open Tree of Life project to link taxonomic information across databases, providing a framework for straightforward comparison of published phylogenies with their updated versions.
<!-- the conflict Application Programming Interface (API) function of  the Open Tree of Life project-->

### 2020-07-30 2-body.Rmd

A way to incorporate the best of two worlds (massive amounts of newly released molecular data and fine-grained curation from human experts) is to rely on published manually curated homology hypotheses as "jump-start" alignments [@morrison2006multiple]. The TreeBASE database [@piel2009treebase] hosts about 8, 200 publicly accesible alignments, providing information on evolutionary relationships of around 100, 000 distinct taxa [(see TreeBASE's website about)](https://www.treebase.org/treebase-web/home.html#:~:text=TreeBASE%20is%20produced%20and%20governed,mapped%20to%20104%2C593%20distinct%20taxa.), representing a source of valuable expert knowledge. Linking these alignments with data from molecular databases that has not yet been included in any public phylogenetic estimate, has the potential to enrich and update phylogenetic relationships in many regions of the tree of life. The phylogenies associated to all these alignments have been integrated to the OpenTree's datastore, the Phylesystem [@mctavish2015phylesystem], and metadata linking these trees to their corresponding alignment repository in TreeBASE is available.
<!-- However, if there are multiple alignments and trees, TreeBASE does not always indicate how they are connected. Hence, Phylesystem's metadata only provides a loose means of linking the tree with the exact alignment that generated it and a human curator must make the link. -->

>>>>

A way to incorporate the best of two worlds (massive amounts of newly released molecular data and fine-grained curation from human experts) is to rely on published manually curated homology hypotheses as "jump-start" alignments [@morrison2006multiple]. The TreeBASE database [@piel2009treebase] hosts about 8, 200 publicly accessible alignments, providing information on evolutionary relationships of around 100, 000 distinct taxa [(see TreeBASE's website about)](https://www.treebase.org/treebase-web/home.html#:~:text=TreeBASE%20is%20produced%20and%20governed,mapped%20to%20104%2C593%20distinct%20taxa.), representing a source of valuable expert knowledge. Linking these alignments with data from molecular databases that has not yet been included in any public phylogenetic estimate, has the potential to enrich and update phylogenetic relationships in many regions of the tree of life. The phylogenies associated to all these alignments have been integrated to the OpenTree's datastore, the Phylesystem [@mctavish2015phylesystem], and metadata linking these trees to their corresponding alignment repository in TreeBASE is available.
<!-- However, if there are multiple alignments and trees, TreeBASE does not always indicate how they are connected. Hence, Phylesystem's metadata only provides a loose means of linking the tree with the exact alignment that generated it and a human curator must make the link. -->
